SILVR: Conditional diffusion model for molecule generation without additional training

### 2023-03-17 paper/manuscript.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[SILVR: Molecular Generation for binding modes]
  {SILVR: Conditional diffusion model for molecule generation without additional training}
\title[SILVR: Molecular Generation for binding modes]
  {SILVR:Directed Diffusion for Molecule Generation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{}
\keywords{ML, generative models, docking}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
One of the challenges as part of computer aided drug-design is to sample from the very large space of possible drug-like compounds to find suitable hits for a given target protein. It is estimated that there are between $10^23$ to $10^60$ possibly feasible compounds, while only around $10^8$ have been synthesised so far~\cite{polishchuk2013estimation, reymond2012exploring}. Different strategies have been employed in the past to try and sample a diverse and synthetically accessible molecular space. In particular, methods based on machine-learning have shown vast amount of promise in recent years in this space~\cite{bilodeau2022generative}. Various different neural network architectures have been proposed for molecular generation, from Varational autoencoders (VAE)~\cite{kingma2022autoencoding, jin2018junction, ma2018constrained}, to generative adversarial networks (GAN)~\cite{hoffmann2019generating} and normalising flows~\cite{shi2021learning}. More recently denoising difusion probailistic models, and particularly equivarient diffusion models have shown promise in moleculear generation~\cite{xu2022geodiff, hoogeboom2022equivariant}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[SILVR: Molecular Generation for binding modes]
  {SILVR: Conditional diffusion model for molecule generation without additional training}
\title[SILVR: Molecular Generation for binding modes]
  {SILVR: Directed (Guided?) Diffusion for Molecule Generation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{}
\keywords{ML, generative models, docking}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
One of the challenges as part of computer aided drug-design is to sample from the very large space of possible drug-like compounds to find suitable hits for a given target protein. It is estimated that there are between $10^{23}$ to $10^{60}$ possibly feasible compounds, while only around $10^8$ have been synthesised so far~\cite{polishchuk2013estimation, reymond2012exploring}. Different strategies have been employed in the past to try and sample a diverse and synthetically accessible molecular space. In particular, methods based on machine-learning have shown vast amount of promise in recent years in this space~\cite{bilodeau2022generative}. Various different neural network architectures have been proposed for molecular generation, from Varational autoencoders (VAE)~\cite{kingma2022autoencoding, jin2018junction, ma2018constrained}, to generative adversarial networks (GAN)~\cite{hoffmann2019generating} and normalising flows~\cite{shi2021learning}. More recently denoising difusion probailistic models, and particularly equivarient diffusion models have shown promise in moleculear generation~\cite{xu2022geodiff, hoogeboom2022equivariant}.
